DV Adjustment

### 2025-04-22 ProjectBlog/Ipynb/Ipynb/ipynb.qmd
p1 plot and CHITA Slides

---
title: "Dobbs' Decision And Abortion2"
date: 01/05/2025
date-modified: last-modified
draft: false
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
    default-image-extension: svg
bibliography: references.bib
---

>>>>

---
title: "Dobbs' Decision And Abortion"
date: 01/05/2025
date-modified: last-modified
draft: false
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: ipynb
---

### 2025-04-22 ProjectBlog/paper2/DV Adjust/DV Adjust.qmd
p1 plot and CHITA Slides

Distribution of going to be times.

@@

Distribution of waking up times.

@@

>>>>

## Distribution of Going to Bed Times

@@

It is not likely that social network activation affects screen time **right before sleep**.

## Distribution of Waking Up Times

@@

## Results with 24 hours Screen Time Measurement

![](images/clipboard-1540611184.png){fig-align="center"}

## Screen Time \< 21:00

![](images/clipboard-2412859547.png){fig-align="center"}

Results with Lagged Core Number

![](images/clipboard-310908795.png){fig-align="center"}

## Potential Mediation Effects

![](images/clipboard-4063857286.png){fig-align="center"}
